---
title: "Assignment_3_final"
author: "Janis Cheng" 
date: "Jan 28th, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Project Info

This project is created on Jan 28th, 2021 for an assignment. It is linked to my [GitHub repository](https://github.com/janischeng0616/Assignment_3.git). My name is Janis Cheng.

### Loading the Data
```{r}
setwd("/Users/janischeng/Desktop/BIO432/Assignments/Assignment3/InputData/")#set directory
MyData<-read.csv("FallopiaData.csv") #load data
head(MyData) 
library(dplyr) #load the dplyr library
```

### Remove rows with ‘Total’ biomass < 60
```{r}
MyData <- filter (MyData,Total >=60) 
```

### Reordering the columns
```{r}
MyData <- select(MyData, Total, Taxon, Scenario, Nutrients)
```

### Making a new column "TotalG" that contains the original "Total" column but in grams
```{r}
MyData<- transmute(MyData, TotalG = Total/1000, Taxon, Scenario, Nutrients)
head(MyData)
```

### Custom Function
```{r}
fx1 <- function(Data, Action) { #ask for input Data and the calculation
  if (Action =='Average') { #Average action, takes mean
    result<- mean(Data)
  } else if (Action =='Sum') { #Sum action, takes sum
    result<- sum(Data)
  } else if (Action =='Observations') { #Observations action, takes number of observations
    result<- NROW(Data)
  } else {
    result<- c("Error") #everything else is error
  }
  return(result)
}
```

### Using the Function
```{r}
fx1 (MyData$Taxon, "Observations") #total number of observations in the 'Taxon' column
fx1 (MyData$TotalG [which(MyData$Nutrients=='low')], "Average") #totalG average for low nutrients
fx1 (MyData$TotalG [which(MyData$Nutrients=='high')], "Average") #totalG average for high nutrients
```

### Saving It Into A New File
```{r}
write.csv(MyData,"/Users/janischeng/Desktop/BIO432/Assignments/Assignment3/WrangledData.csv", row.names = FALSE)#Write (i.e. save) the new data to a file called "WrangledData.csv" in the Output folder. 
```
